---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit this file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "man/figures/",
  fig.retina = 3
)
```

## sdApps

The `sdApps` package is a collection of companion applications that support the [surveydown](https://surveydown.org/) survey platform.

## Installation

The `sdApps` package is not yet on CRAN, but the development version can be installed from GitHub:

```{r}
#| eval: false

# install.packages("pak")
pak::pak("surveydown-dev/sdApps", ask = FALSE)
```

## Launch the Studio

The **surveydown Studio** is a unified Shiny application that provides both survey creation and data management capabilities. The studio includes four main tabs:

- **Construction**: GUI for creating and editing surveys
- **Preview**: Live preview of your survey
- **Dashboard**: View and analyze survey response data
- **Settings**: Database connection configuration

To launch the studio, run the following in the R console:

```{r}
#| eval: false

sdApps::sd_studio()
```
