---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit this file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "man/figures/",
  fig.retina = 3
)
```

## sdApps

The `sdApps` package is a collection of companion applications that support the [surveydown](https://surveydown.org/) survey platform.

## Installation

The `sdApps` package is not yet on CRAN, but the development version can be installed from GitHub:

```{r}
#| eval: false

# install.packages("pak")
pak::pak('surveydown-dev/sdApps)
```

## Dashboard

The **surveydown Dashboard** is a Shiny application that provides a user-friendly interface for managing and viewing survey response data from live surveys. To launch the dashboard, run the following in the R console:

```{r}
#| eval: false

sdApps::sd_dashboard()
```

## Studio

The **surveydown Studio** is a Shiny application that provides a GUI for creating and managing surveys. To launch the dashboard, run the following in the R console:

```{r}
#| eval: false

sdApps::sd_studio()
```
