---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit this file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "man/figures/",
  fig.retina = 3
)
```

## sdApps

The `sdApps` package provides companion Shiny applications that support the [surveydown](https://surveydown.org/) survey platform. It transforms the typical code-heavy survey creation workflow into an accessible GUI interface, making it easy to create, preview, and manage surveys without extensive programming knowledge.

## Installation

The `sdApps` package is not yet on CRAN, but the development version can be installed from GitHub:

```{r}
#| eval: false

# install.packages("pak")
pak::pak("surveydown-dev/sdApps", ask = FALSE)
```

## surveydown Studio

The **surveydown Studio** is the main application in sdApps - a unified Shiny interface for complete survey lifecycle management. Launch it with:

```{r}
#| eval: false

sdApps::sd_studio()
```

### Studio Features

#### 🏗️ **Build Tab** - Visual Survey Creation
- **Drag-and-drop interface** for intuitive survey construction
- **15 survey templates** covering basic to advanced use cases:
  - Basic templates (Default, Question Types, YAML-based)
  - Advanced features (Conditional logic, Random options, Reactive questions)
  - Specialized surveys (Conjoint experiments, Interactive maps, Live polling)
- **Dual-pane editor** with visual builder and code editor (ACE integration)
- **12 question types** including multiple choice, text, numeric, sliders, dates
- **Real-time synchronization** between visual interface and underlying code
- **Undo/redo functionality** for all editing operations
- **Local/Live mode switching** for development and production workflows

#### 👁️ **Preview Tab** - Live Survey Testing  
- **Real-time preview** of your survey as you build
- **Responsive preview modes**: Desktop (widescreen) and Mobile (375px) views
- **Automatic refresh** when survey code changes
- **Interactive testing** environment before deployment

#### 📊 **Responses Tab** - Data Management & Analytics
- **PostgreSQL database integration** with connection pooling
- **GSSAPI encryption support** with automatic fallback options
- **Real-time analytics dashboard** showing:
  - Total responses and daily averages
  - Completion rate tracking
  - Cumulative and daily response trends (interactive charts)
- **Interactive data table** with search, filtering, and sorting
- **CSV export functionality** for data analysis
- **Visual connection status** indicators with detailed feedback

### Key Capabilities

**Template System**: Choose from 15 professionally designed templates ranging from basic surveys to advanced conjoint experiments and interactive visualizations.

**Visual Survey Builder**: Create surveys using an intuitive drag-and-drop interface with real-time code synchronization, eliminating the need for manual coding while maintaining full code access.

**Database Integration**: Seamless PostgreSQL connectivity with enterprise-grade security (GSSAPI encryption) and automatic connection management.

**Responsive Design**: Built with Bootstrap 5, providing a modern, mobile-friendly interface that works across all devices.

**Development Workflow**: Switch between Local (development) and Live (production) modes with one click, supporting iterative survey development and testing.

## Database Configuration

The studio supports flexible database connection modes:

```{r}
#| eval: false

# Auto mode (recommended) - tries GSSAPI first, falls back if needed
sd_studio()

# Prefer mode - uses GSSAPI if available, plain connection if not  
sd_studio(gssencmode = "prefer")

# Disable mode - forces plain connection (useful for VPN environments)
sd_studio(gssencmode = "disable")
```

Configure your database connection using environment variables or the built-in Settings interface within the studio.
